### 2012-08-24 inst/examples/unmanaged_warning.Rmd
initial signals for unmanaged case. #21

@@

``` {r parallel}
library(snow)
library(methods)
cl <- makeCluster(20, type = "MPI")
clusterEvalQ(cl, library(earlywarning))
```

>>>>

``` {r  p1}
plot(y, type='l')
````

@@

``` {r parallel}
library(snow)
library(methods)
#cl <- makeCluster(20, type = "MPI")
#clusterEvalQ(cl, library(earlywarning))
#clusterExport(cl, ls())
#clusterExport(cl, list = c("A", "B"))
require(snowfall)
sfInit(par=T, cpu=12)
sfLibrary(earlywarning)
sfExportAll() 
```

Evaluate the ROC curve

``` {r roc}
reps <- sfLapply(1:500, function(i) compare(A, B))
lr <- lik_ratios(reps)
roc <- roc_data(lr)
```

Plot results.

``` {r plotroc}
require(ggplot2)
ggplot(lr) + geom_density(aes(value, fill = simulation), alpha = 0.6) + 
    geom_vline(aes(xintercept = observed))
ggplot(roc) + geom_line(aes(False.positives, True.positives))
```
